---
title: "HW2_Yeonji_Frankie_Ofer"
author: "Yeonji Jung, Frankie Tam, Ofer Chen"
date: "10/2/2018"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1 

```{r}
#Loading relevant libraries
library(tidyverse)
library(lubridate)
library(aod)
```

```{r}
#Reading data
exit_poll <- read_tsv("poll_data.tsv")
exit_poll <- as.tibble(exit_poll)
dim(exit_poll)
```
## Part B
```{r}
#Rename vote_2008 to candidate and convert to factor
exit_poll <- exit_poll %>% mutate(candidate = as.factor(vote_2008)) %>% select(-vote_2008) %>% slice(sample(1:n()))

#Perform logistic regression
vote_model <- glm(candidate ~ state + sex + race + age + education + party + ideology + state_contestedness, family = "binomial", data = exit_poll)

#str(vote_model)
```

```{r}
#Examine model
summary(vote_model)
```

### i) 
Coefficients for each age group and gender
sexmale 0.0232138
age30-44 0.3452590
age45-64 0.4093395
age65+ 0.3464339
       
since sex and age are categorical variables, sex-female and age18-29 are being used as reference category for their respective variables. This is the reason for sexfemale and age18-29 are not being shown in the model explicitly.

### ii)

According to p-value of the variables, sexmale is 0.709 and it is not statistically significant. On the other hand, p-value of age variables are 0.0003, 7.33e-06 and 0.0021. They are statistically significant. According to the coefficients, it indicates when comparing voters in age30-44 bracket to age 18-29, the odds of voting for mcCain increase by a factor of 0.345. When comparing voters in age45-64 bracket to age 18-29, the odds of voting for mcCain increase by a factor of 0.409. Lastly, when comparing voters in age65+ bracket to age 18-29, the odds of voting for mcCain increase by a factor of 0.346.

Other than age, race, ideology, party, education except didn't graduate from high school and six particular states are also statistically significant.

### iii)
```{r}
#Run prediction
vote_probs=predict(vote_model,type="response")
vote_probs[1:10]
#Check representation of 0 and 1 value
contrasts(exit_poll$candidate)
```
```{r}
vote_pred=rep("barack obama", 5113)
vote_pred[vote_probs>.5]="john mcCain"
vote_pred_table <- table(vote_pred, exit_poll$candidate)
vote_pred_table
```

```{r}
#Compute accuracy
accuracy <- sum(diag(vote_pred_table))/sum(vote_pred_table)
#Compute precision
# TP/(TP+FP)
precision <- diag(vote_pred_table)/colSums(vote_pred_table)
#Compute recall
# TP/(TP+FN)
recall <- diag(vote_pred_table)/rowSums(vote_pred_table)

accuracy
data.frame(precision, recall)
```


### iv)
```{r}
vote_pred_t70=rep("john mcCain", 5113)
vote_pred_t70[(1-vote_probs)>.7]="barack obama"
vote_pred_table_t70 <- table(vote_pred_t70, exit_poll$candidate)
vote_pred_table_t70
```
```{r}
#Compute accuracy
accuracy_t70 <- sum(diag(vote_pred_table_t70))/sum(vote_pred_table_t70)
#Compute precision
# TP/(TP+FP)
precision_t70 <- diag(vote_pred_table_t70)/colSums(vote_pred_table_t70)
#Compute recall
# TP/(TP+FN)
recall_t70 <- diag(vote_pred_table_t70)/rowSums(vote_pred_table_t70)

accuracy_t70
data.frame(precision_t70, recall_t70)
```

Accuracy goes up from 0.8558 to 0.8595. Precision for predicting vote for obama goes up from 0.814 to 0.872 while recall also goes up from 0.86 to 0.92. On the other hand, precision for predicting vote for mcCain goes down from 0.89 to 0.82 and recall goes down from 0.85 to 0.73.

## Part C

```{r}

```

