---
title: "HW2_Yeonji_Frankie_Ofer"
author: "Yeonji Jung, Frankie Tam, Ofer Chen"
date: "10/2/2018"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1 

```{r}
#Loading relevant libraries
library(tidyverse)
library(lubridate)
library(aod)
```

```{r}
#Reading data
exit_poll <- read_tsv("poll_data.tsv")
exit_poll <- as.tibble(exit_poll)
dim(exit_poll)
```
## Part B
```{r}
#Rename vote_2008 to candidate and convert to factor
exit_poll <- exit_poll %>% mutate(candidate = as.factor(vote_2008)) %>% select(-vote_2008) %>% slice(sample(1:n()))

#Perform logistic regression
vote_model <- glm(candidate ~ state + sex + race + age + education + party + ideology + state_contestedness, family = "binomial", data = exit_poll)

#str(vote_model)
```

```{r}
#Examine model
summary(vote_model)
```

### i) 
Coefficients for each age group and gender
sexmale 0.0232138
age30-44 0.3452590
age45-64 0.4093395
age65+ 0.3464339
       
since sex and age are categorical variables, sex-female and age18-29 are being used as reference category for their respective variables. This is the reason for sexfemale and age18-29 are not being shown in the model explicitly.

### ii)

According to p-value of the variables, sexmale is 0.709 and it is not statistically significant. On the other hand, p-value of age variables are 0.0003, 7.33e-06 and 0.0021. They are statistically significant. According to the coefficients, it indicates when comparing voters in age30-44 bracket to age 18-29, the odds of voting for mcCain increase by a factor of 0.345. When comparing voters in age45-64 bracket to age 18-29, the odds of voting for mcCain increase by a factor of 0.409. Lastly, when comparing voters in age65+ bracket to age 18-29, the odds of voting for mcCain increase by a factor of 0.346.

Other than age, race, ideology, party, education except didn't graduate from high school and six particular states are also statistically significant.

### iii)
```{r}
#Run prediction
vote_probs=predict(vote_model,type="response")
vote_probs[1:10]
#Check representation of 0 and 1 value
contrasts(exit_poll$candidate)
```

```{r}
vote_pred=rep("barack obama", 5113)
vote_pred[vote_probs>.5]="john mcCain"
vote_pred_table <- table(vote_pred, exit_poll$candidate)
vote_pred_table
```

```{r}
#Compute accuracy
accuracy <- sum(diag(vote_pred_table))/sum(vote_pred_table)
#Compute precision
# TP/(TP+FP)
precision <- diag(vote_pred_table)/colSums(vote_pred_table)
#Compute recall
# TP/(TP+FN)
recall <- diag(vote_pred_table)/rowSums(vote_pred_table)

accuracy
data.frame(precision, recall)
```


### iv)
```{r}
vote_pred_t70=rep("john mcCain", 5113)
vote_pred_t70[(1-vote_probs)>.7]="barack obama"
vote_pred_table_t70 <- table(vote_pred_t70, exit_poll$candidate)
vote_pred_table_t70
```
```{r}
#Compute accuracy
accuracy_t70 <- sum(diag(vote_pred_table_t70))/sum(vote_pred_table_t70)
#Compute precision
# TP/(TP+FP)
precision_t70 <- diag(vote_pred_table_t70)/colSums(vote_pred_table_t70)
#Compute recall
# TP/(TP+FN)
recall_t70 <- diag(vote_pred_table_t70)/rowSums(vote_pred_table_t70)

accuracy_t70
data.frame(precision_t70, recall_t70)
```

Accuracy goes up from 0.8558 to 0.8595. Precision for predicting vote for obama goes up from 0.814 to 0.872 while recall also goes up from 0.86 to 0.92. On the other hand, precision for predicting vote for mcCain goes down from 0.89 to 0.82 and recall goes down from 0.85 to 0.73.

## Part C

## Question 1.C.i

```{r}
#pulling full poll data file
poll_data_full <- read.delim("poll_data_full.tsv")
#creating a major party boolean variable
poll_data_full <- mutate(poll_data_full, major_party= if_else(poll_data_full$vote_2008 %in% c("john mcCain","barack obama"),1,0))
#Creating a logistic regression on likelihood to vote for a major party candidate 
myvote_full <- glm(major_party ~ state + sex + race + age + education + party + ideology + state_contestedness, data = poll_data_full, family = "binomial")
#Using the model to predict the probabilities for major party votes
major_prediction <- predict(myvote_full, type = 'response')
summary(major_prediction)
#Plotting major party votes on a histogram
hist(major_prediction, xlab = "Probability of voting for a major party candidate", main = "Histogram of probability of voting for a major party candidate", breaks = 200)
```
## Question 1.C.ii

```{r}
#Filtering revised exit poll data to major party voters
poll_data_filtered <- poll_data_full %>% filter(poll_data_full$major_party==1) %>% select(-major_party)
# creating a Boolean variable for voting Obama
poll_data_filtered$obama_vote <- poll_data_filtered$vote_2008=="barack obama"
#Logistic regression over chances to vote McCain -- by some default McCain is 1 and Obama is 0
obama_model <- glm(obama_vote ~ state + sex + race + age + education + party + ideology + state_contestedness, data =poll_data_filtered, family = "binomial")
```

#question 1.C.iii
```{r}
#Creating the prediction
poll_data_filtered$obama_prediction <- predict(obama_model,type = 'response')
#PLotting
hist(poll_data_filtered$obama_prediction, xlab = "P(obama|major_party)", main = "Histogram of P(obama|major_party)", breaks = 200)


```

#question 1.C.iv
```{r}
# creating the relevant prediction variables
poll_data_full$pred_other_prob <- 1-major_prediction
poll_data_full$pred_obama_prob <- predict(obama_model,poll_data_full, type = 'response')
poll_data_full$pred_mccain_prob <- 1-poll_data_full$pred_other_prob-poll_data_full$pred_obama_prob
poll_data_full$pred_mccain_prob <- if_else(poll_data_full$pred_mccain_prob<0, 0, poll_data_full$pred_mccain_prob)

#Creating categorical predictions
```


